\documentclass[12pt]{article}

\begin{document}

\title{PocketAlchemy Features List - v0.1.alpha}
\author{Cody J. Weaver}
\date{Dec. 31th 2023}
\maketitle

\begin{center}
    \indent This document will give an overview of the features currently functional in 
    v0.1.alpha and document the planned features for v0.2.alpha.

    \section*{Current Features}

    \indent The following features are available in PocketAlchemy
    v0.1.alpha.

    \begin{itemize}
        \item User should be able to create recipe with title, 
        subtitle, and description.

        \item User should be able to edit their recipes.
        
        \item User should be able to log in anonymously and have their
        data persist.
    \end{itemize}

    \section*{Planned Features}

    \indent PocketAlchemy v0.2.alpha is planned to have the following
    features available.

    \begin{itemize}
        \item User should be able to view a recipe's details 
        in a distinct view from editing a recipe. Without the ability
        to edit the recipe, the view should present a more streamlined view of 
        the recipes details. 

        \item A user should be able to navigate to edit a recipe from a
        read only view of that recipe's details.

        \item User should be able to filter their recipes by all fields 
        currently implemented in recipe model.

        \item User can add ingredients to recipes, with information 
        of ingredient name and quantity.


    \end{itemize}

\end{center}

\end{document}
